Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2014-08-08 figures/model-pdd.tex
Adjust figure widths.

% background
\fill[white] (-0.25,-0.25) rectangle +(8.5,14.75);
%\draw[help lines, lightgray] (0,0) grid (8,14);

% add nodes
\path     (4, 13.75) node [trunk] (acc) {Compute snow accumulation, $A_s$}
  -- ++(0, -1.5) node [trunk] (pdd) {Compute PDDs}
  -- ++(0, -1.5) node [trunk]  (s1) {Update snow depth \\
                                      $S \gets S + A_s$}
  -- ++(0, -1.5) node [trunk] (msp) {Compute potential snow melt \\
                                      $M_{s,p} := \PDD \times F_{s}$}
  -- ++(0, -2.25) node [split] (split) {$M_{s,p} > H_s?$};

>>>>

% background
\fill[white] (0,0) rectangle +(8.0,14.75);
%\draw[help lines, lightgray] (0,0) grid (8,14);

% add nodes
\path     (4, 14) node [trunk] (acc) {Compute snow accumulation, $A_s$}
  -- ++(0, -1.5) node [trunk] (pdd) {Compute PDDs}
  -- ++(0, -1.5) node [trunk]  (s1) {Update snow depth \\
                                      $S \gets S + A_s$}
  -- ++(0, -1.5) node [trunk] (msp) {Compute potential snow melt \\
                                      $M_{s,p} := \PDD \times F_{s}$}
  -- ++(0, -2.25) node [split] (split) {$M_{s,p} > H_s?$};
